Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-18 ms.tex
doubled sections are removed
numbers are re-checked...

@@

Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary). 
%
They are compared with numerical simulations in \citet{christensen2010}. We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
%%%%%%%%%% 
\begin{equation}
B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
\end{equation}
%%%%%%%%%%
where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.

@@

The convected heat flux, $q_c$, is estimated by dividing the time-dependent net planetary luminosity by the surface area of the core region ($4\pi r_c^2$). 
The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
%%%%%%%%%%
\begin{equation}
L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
\memoYF{Burrows et al. 2001 says $10^{-9} L_\odot $, but it looks to me like it is actually $10^{-8} L_\odot $}. 
%We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}, which is used for the scaling of planetary magnetic fields.

\memoYF{I am not sure if the following paragraph is needed.}
There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
%%%%%%%%%% 
\begin{equation}
\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
%
Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants. Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr]. 
\memoYF{Would their spin rate become higher or lower??}
\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}

@@

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griebmeier2007}. 
%, following the procedure of \citet{griebmeier2007}. 
This is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
\end{eqnarray}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
Because... \memoYF{I want to justify not to consider the magnetic case.}, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.

@@

Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
\end{eqnarray}
%%%

Now, we compare radio emission power of canonical hot jupiters and that of red giant hot jupiters. 
Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. 
Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows. 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
&\approx & 460 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%%
Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission will be even weaker. 
\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
\memoYF{what is the typical wind velocity of AGB stars?}

@@

Then, spectral radio flux observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
%&=& P_{\rm radio,\,J} \\
&\approx & 5.4\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
%%%
&\approx & 1.2 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
%%%
&\approx & 1.2 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.5 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
%\\
%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
\end{eqnarray}
%%%
Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}. 
Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.

@@

Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
%%%
\begin{eqnarray}
F_{\nu} &<& 8 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right) \\
&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
\end{eqnarray}
%%%
Since the dependence of the mass-loss rate is weak, even for evolved stars with significant mass loss rate (e.g. AGB stars), the upper limit of the stellar flux would not be changed by orders of magnitude. 
Thus, we may consider that the radio-brightest planetary systems at 10 pc would emit $\sim 10^{-2}$ Jy.

>>>>

\memoYF{In the end the number of significant decimal digits is set to 1 or 2.}

@@

Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griebmeier2004} or \citet{christensen2010} for the summary). 
%
They are compared with numerical simulations in \citet{christensen2010}. We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
%%%%%%%%%% 
\begin{equation}
B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
\end{equation}
%%%%%%%%%%
where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G by equation (\ref{eq:Bscaling}).

@@

The convected heat flux, $q_c$, is estimated by dividing the time-dependent net planetary luminosity by the surface area of the core region ($4\pi r_c^2$). 
The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
%%%%%%%%%%
\begin{equation}
L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
\memoYF{Burrows et al. 2001 says $10^{-9} L_\odot $, but it looks to me like it is actually $10^{-8} L_\odot $}. 
%We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$. 
%The internal heat flux of Jupiter is  $q_{c,\,J} \sim 5.4\,{\rm [W/m^2]}$ \citep{hanel1981}; this leads to the Jovian magnetic field $B_J \sim $
is used for the scaling of planetary magnetic fields.

\memoYF{I am not sure if the following paragraph is needed.}
There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
In particular, \citet{griebmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
%%%%%%%%%% 
\begin{equation}
\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
%In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}
%
Unlike usual hot jupiters, RGHJsEst are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants. Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr]. 
%\memoYF{Would their spin rate become higher or lower??}
%\memoDS{There's no reason to suspect either, although more massive planets might spin faster.}

@@

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griebmeier2007}. 
%, following the procedure of \citet{griebmeier2007}. 
This is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
\end{eqnarray}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
%
In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
Because... \memoYF{I want to justify not to consider the magnetic case.}, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.

@@

Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
\end{eqnarray}
%%%

Now, we compare radio emission power of canonical hot jupiters and that of red giant hot jupiters. 
Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. 
Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows. 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%%
Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission will be even weaker. 
\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
\memoYF{what is the typical wind velocity of AGB stars?}

@@

Then, spectral radio flux observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
%&=& P_{\rm radio,\,J} \\
&\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
%%%
&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
%%%
&\approx & 1.12 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
%\\
%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
\end{eqnarray}
%%%
Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}. 
Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.

@@

Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
%%%
\begin{eqnarray}
F_{\nu} &<& 8 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right) \\
&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{-1}  \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{1/6} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
\end{eqnarray}
%%%
%Since the dependence of the mass-loss rate is weak, even for evolved stars with significant mass loss rate (e.g. AGB stars), the upper limit of the stellar flux would not be changed by orders of magnitude. 
%Thus, we may consider that the radio-brightest planetary systems at 10 pc would emit $\sim 10^{-2}$ Jy.
